---
title: "viewCityMap"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{viewCityMap}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
runtime: shiny
---

## Introduction and the viewCityMap() Function

The package *viewCityMap* allows users to pull a map of any city in United States. The function **viewCityMap()** takes the name of a city and state as inputs, and it uses this information to plot a map of the city and the surrounding area using Stamen Maps API. **Please note:** the function uses the full name of both the city and state to match the internal data set being used, abbreviations will result in an error. Users are also able to select the type of map they want to see, based on the options available from Stamen Maps. The default is "toner-hybrid," but users may choose from the following options: "terrain", "terrain-background", "terrain-labels", "terrain-lines", "toner", "toner-2010", "toner-2011", "toner-background", "toner-hybrid", "toner-labels", "toner-lines", "toner-lite", "watercolor"

To illustrate output of this function, let's look at the default map of Albany, New York

```{r}
library(viewCityMap)
viewCityMap("Albany","New York")

```

## The viewCityMap Shiny App

The **viewCityMap** package also comes with a Shiny app that provides a graphical interface for users to request a map.
To load this app, run the following command in the console:

```{r, eval = FALSE}
runGitHub("viewCityMap","infobambaranda",subdir = "inst/app")
```

This will open the menu shown below. There are three drop down menus where users can select the city, state, and map type they would like to see. When the "Show Map!" button is clicked, the relevant map will be loaded (and will be shown until a new map request is made. To search for a specific city, start typing the name of the city in the input box marked "City Name" and choose from the options shown in the drop down menu.

```{r, echo=FALSE}
shiny::selectInput("cn", "City name:", choices= c("Albany"), selected = "Albany")
shiny::selectInput("st", "State:", choices= c("New York"), selected = "New York")
shiny::selectInput("mp", "Map Type:", choices= c("toner-hybrid"), selected = "toner-hybrid")
shiny::actionButton("show_map", "Show map!")

# map <- viewCityMap("Albany","New York","toner-hybrid")
shiny::renderPlot({viewCityMap("Albany","New York")})
```